Spoken Corpus of Karel Mako\v{n}

### 2018-04-11 2018-clarin-pisa/makon-data.tex
bla
table for clarin 2018

@@

This was a cheap solution for a low-hanging fruit but a more holistic approach
is

>>>>

We can take the current transcription %and the few notes some listeners made
%about topics and their alignment with the audio
as a source for a baseline.
Topic is inherently a vague concept, which I shall address when I focus on it
but for the baseline evaluation, we can take a look at some easily defined cases
like named entities. The ease about them is that we can look for their specific
word form and if it is not found, then it means the transcription is not talking
about it.

Of course, there are exceptions, like saying ``the capital of Japan'' instead of
``Tokyo'' but firstly, I chose terms where this is not likely to happen and
secondly, this can only lower the recall of our baseline score, not the
precision, and we have no way of telling the precision given no annotated data
for this task.\footnote{The 50-minute test set is way too small for this kind of
task.}

I have chosen the following terms:

\begin{enumerate}
\item{Lazarus,}
\item{Mithra, Mithraism,}
\item{Satan,}
\item{St. Teresa,}
\item{fairy-tale.}
\end{enumerate}

I chose fairy-tale (Czech: \emph{poh\'{a}dka}) as a recurring topic with a
unifying word, for an example of a non-named-entity.

The search for stems of these words in the automatic part of the transcription
yielded results summed up in Table~\ref{tab:topicsearch}. For terms where there
were more than 20 hits, I have checked the first 20 but each from a different
file.

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l|l|r|r|r|}
\hline
Term & Query & hits in automatic transcription & hits in manual transcription & Precision \\
\hline
Lazarus & \texttt{lazar.*} & 16 & 14 & 8/10   \\
Mithra & \texttt{mithra.*|mitra.*} & 0 & 0 & n/a   \\
Satan & \texttt{satan.*} & 308 & 129 & 16/20   \\
St. Teresa & \texttt{terez.*} & 882 & 91 & 15/20   \\
fairy-tale & \texttt{pohádk.*} & 216 & 55 & 18/20   \\
\hline
\multicolumn{4}{|l|}{average precision} & 81.25\%\\
\hline
\end{tabular}
\caption{Text search hits in the automatically-acquired part of the
transcription}\label{tab:topicsearch}
\end{center}
\end{table}

@@

This was a cheap solution for a low-hanging fruit but a more holistic approach
is very desirable.

% 7.6\% of the corpus is annotated with 620615 : 7574994 hum : auto
